---
title: "General Social Survey (GSS)"
author: "Peggy Ong"
date: "22 Sep 2014"
output:
  html_document:
    theme: cerulean
---

<!-- For more info on RMarkdown see http://rmarkdown.rstudio.com/ -->
/*  CSS chunck 1  */
th {  background-color:#E0E0E0 ;
      border-bottom:1px solid black;
      padding:5px;}

td{
border-bottom:1px dotted black;
padding:5px;}

table{ 
border-collapse:collapse;
margin:auto;
 border: 1px solid black;}
 
<!-- Enter the code required to load your data in the space below. The data will be loaded but the line of code won't show up in your write up (echo=FALSE) in order to save space-->
```{r echo=FALSE}
load(url("http://bit.ly/dasi_gss_data"))
```

<!-- In the remainder of the document, add R code chunks as needed -->

### Introduction:

A sociological survey used to collect data on demographic characteristics and attitudes of residents of the United States. The codebook below lists all variables, the values they take, and the survey questions associated with them. There are a total of 57,061 cases and 114 variables in this dataset. Note that this is a cumulative data file for surveys conducted between 1972 - 2012 and that not all respondents answered all questions in all years.  
* Codebook: Review the codebook to view a list of all variables, the values they take, and the original survey questions associated with the variables.  
* Use the following code to load the GSS dataset into R:  

### Data:
*Dataset Variables*
```{r echo=FALSE}
names(gss)

```

Insert data section here...

### Exploratory data analysis:

Insert exploratory data analysis here...
``` {r echo=FALSE}
dim(gss)

for (i in 1:length(gss)) { 
     print(names(gss[i]))
     print(summary(gss[,i])) 
}
```
### Inference:

Insert inference section here...

### Conclusion:

Insert conclusion here...
